---
title: "Test Weather"
format: html
editor: visual
---

## Introduction

This notebook demonstrates the different functions that have been developed to analyse and check the weather data from La Corona, based on the original work from Prof Chip Cheshier and Prof Francois Birgand at North Carolina State University.

Scripts and functions have been developed as part of FPTA 358 funded by INIA Uy.

This document specifically focuses on the analysis of the rainfall data

## packages

To be able to run this notebook, the following R packages should be available

```{r message = FALSE}
library(tidyverse) 
library(plotly) 
#library(htmlwidgets)
```

## Loading the developed functions

The functions are stored in the scripts folder, the same folder as the code version of this file (the \*.qmd file).

```{r loadfunctions}
source("Functions_Weather.R") 
```

We can now list all the functions that have been loaded using:

```{r listfunctions}
print(lsf.str())
```

Define the Data directory

```{r}
Data_dir = "..//All_Raw_Data/Test_T4T52023_folder/T042223/Weather"
```

The weather/climate file does not actually contain any column names, so these need to be defined separately.

```{r}
c_names <- c("id", "julian", "time", "battery voltage", 
             "Temperature °C",
             "RelH", "windspeed", "wind direction", "net radiation",
             "solar radiation",   "rainfall")
# columns to drop when you have created the date and time variable
cols_drop <- c("id", "julian", "time", "battery voltage")
```

We can now test the developed functions to read in the weather files and store the data in the processed folder.

```{r test-read-hobo}
test_hobo <- read_hobo_weather(filename = "em042223.dat", 
                         dir = Data_dir,
                               cols_to_drop = cols_drop, plotit=T)
test_hobo$data

ggplotly(test_hobo$plot)

```

**Note that the rainfall in the \*.dat file is always 0**. The rainfall from the weather station is analysed in the test_rainfall.qmd file.

And we can test the ET0 function

```{r check-ET0}
test_ET0 <- ET0_hobo_weather(filename = "em042223.dat", 
                        dir = Data_dir,
                               cols_to_drop = cols_drop, plot_data=T)
test_ET0$data

ggplotly(test_ET0$plot)
```
